Who we are affects how we vote

### 2019-05-06 elections_conversation.Rmd
Working on graphs

@@

```{r plotintercept, fig.cap = "Estimated intercept for each election, which represents the two-party preferred vote for an electorate with average characteristics.", fig.pos="H"}
intercept_df <- bind_rows(
  data.frame(summary(glsmod16)$tTable)[1, ] %>% mutate(year = "2016"),
  data.frame(summary(glsmod13)$tTable)[1, ] %>% mutate(year = "2013"),
  data.frame(summary(glsmod10)$tTable)[1, ] %>% mutate(year = "2010"),
  data.frame(summary(glsmod07)$tTable)[1, ] %>% mutate(year = "2007"),
  data.frame(summary(glsmod04)$tTable)[1, ] %>% mutate(year = "2004"),
  data.frame(summary(glsmod01)$tTable)[1, ] %>% mutate(year = "2001")
) %>%
  rename(se = `Std.Error`, estimate = Value, p = `p.value`) %>%
  mutate(upper95 = estimate + 1.96 * se, lower95 = estimate - 1.96 * se)

intercept_df %>%
  ggplot() +
  geom_point(aes(x = year, y = estimate), size = 3) +
  geom_linerange(aes(x = year, ymin = lower95, ymax = upper95), size = 1.2) +
  geom_hline(aes(yintercept = 50), alpha = 0.5, size = 1) +
  labs(x = "Election year", y = "Estimate of 2PP vote in average electorate") +
  coord_fixed(ratio = 0.2) +
  ylim(45.3, 54.7)
```

@@

## Influential socio-demographics

```{r prepplot, echo = FALSE}
grid_visreg("Extractive", top = TRUE)
grid_visreg("DiffAddress")
grid_visreg("ManagerAdmin")
grid_visreg("Transformative")
grid_visreg("Incomes")
grid_visreg("Unemployment")
grid_visreg("MedianAge", top = TRUE)
grid_visreg("Judaism")
grid_visreg("OtherLanguage")
grid_visreg("OtherLanguage")
grid_visreg("BornAsia")
grid_visreg("Education")
grid_visreg("BornSEEuro")
grid_visreg("DeFacto")
```

Partial residual plots by election year for a selection of predictors. Linear model with 95\\% confidence bands overlaid. Most predictors have a positive relationship: the larger the value the more likely the electorate preferences the Coalition. The relationship is relatively robust over time, with the exception of Unemployment.

Several predictors have a negative relationship: with larger values indicating the electorate more likely preferences Labor. Most relationships are relatively stable over elections, except OtherLanguage and Education.

To investigate the socio-demographics that have a strong effect on the two-party preferred vote, partial residual plots are used and shown in Figures \@ref(fig:partresplot1) and \@ref(fig:partresplot2). The partial residuals are the residuals from the fitted model with the estimated effect an individual variable added. These show the direction, size and significance of an estimated effect --- the slope of the prediction line matches the estimated coefficient, and the shaded region represents a 95% confidence band, computed using the method in @visreg. If a horizontal line can be drawn through the confidence band, then the effect is insignificant. The estimated intercept is also added to the partial residuals for interpretability. Plots for each election are faceted to compare the effects over time in Figures \@ref(fig:partresplot1) and \@ref(fig:partresplot2). Only socio-demographics that have a significant effect in at least one election are displayed in Figures \@ref(fig:partresplot1) and \@ref(fig:partresplot2).

@@

@@

>>>>

```{r coefficients}
coefs <- bind_rows(
    data.frame(summary(glsmod16)$tTable) %>% 
      rownames_to_column("variable") %>%
      mutate(year = 2016),
    data.frame(summary(glsmod13)$tTable) %>% 
      rownames_to_column("variable") %>%
      mutate(year = 2013),
    data.frame(summary(glsmod10)$tTable) %>% 
      rownames_to_column("variable") %>%
      mutate(year = 2010),
    data.frame(summary(glsmod07)$tTable) %>% 
      rownames_to_column("variable") %>%
      mutate(year = 2007),
    data.frame(summary(glsmod04)$tTable) %>% 
      rownames_to_column("variable") %>%
      mutate(year = 2004),
    data.frame(summary(glsmod01)$tTable) %>% 
      rownames_to_column("variable") %>%
      mutate(year = 2001)
  ) %>%
  as_tibble() %>%
  rename(se = `Std.Error`, estimate = Value, p = `p.value`) %>%
  mutate(upper95 = estimate + 1.96 * se, lower95 = estimate - 1.96 * se)
```

@@

```{r plotintercept, fig.cap = "Estimated intercept for each election, which represents the two-party preferred vote for an electorate with average characteristics.", fig.pos="H"}
coefs %>% filter(variable=="Intercept") %>%
  ggplot() +
  geom_point(aes(x = year, y = estimate), size = 2) +
  geom_linerange(aes(x = year, ymin = lower95, ymax = upper95), size = 1.2) +
  geom_hline(aes(yintercept = 50), alpha = 0.5, size = 1) +
  labs(x = "Election year", y = "2PP percentage") +
  coord_fixed(ratio = 0.25) +
  scale_x_continuous(breaks=seq(2001,2016,by=3), minor_breaks=NULL) +
  scale_y_continuous(breaks=seq(46,54,by=2), minor_breaks=45:55)
```

@@

@@

## Age

- Would it be possible to show how the correlation changes for different age brackets (ie. younger voters = more Labor, and this swings more to Liberal as the age brackets gets older)?
- If not, can you go into more detail specific age brackets? Eg. Is it the over-65s that skew Liberal?

```{r age, fig.cap = "Estimated age effect for each election, which represents the impact of electorate median age on the two-party preferred vote. Higher values indicate a ", fig.pos="H"}
coefs %>% filter(variable=="MedianAge") %>%
  ggplot(aes(x=year)) +
  geom_hline(aes(yintercept = 0), col='gray', size = 1) +
  geom_point(aes(x = year, y = estimate), size = 2) +
  geom_linerange(aes(x = year, ymin = lower95, ymax = upper95), size = 1.2) +
  labs(x = "Election year", y = "2PP impact") +
  coord_fixed(ratio = 0.25) + 
  scale_x_continuous(breaks=seq(2001,2016,by=3), minor_breaks=NULL)
```

@@

```{r age, fig.cap = "Estimated age effect for each election, which represents the impact of electorate median age on the two-party preferred vote. Higher values indicate a ", fig.pos="H"}
coefs %>% filter(variable=="MedianAge") %>%
  ggplot(aes(x=year)) +
  geom_hline(aes(yintercept = 0), col='gray', size = 1) +
  geom_point(aes(x = year, y = estimate), size = 2) +
  geom_linerange(aes(x = year, ymin = lower95, ymax = upper95), size = 1.2) +
  labs(x = "Election year", y = "2PP impact") +
  coord_fixed(ratio = 0.25) + 
  scale_x_continuous(breaks=seq(2001,2016,by=3), minor_breaks=NULL)
```

### 2019-05-06 elections_conversation.tex
Working on graphs

\usepackage[no-weekday]{eukdate}
%\usepackage{sourceserifpro}
%\usepackage[scaled=0.86]{DejaVuSansMono}
\usepackage{float,bm,setspace}
\setstretch{1.2}

@@

@@

@@

\hypertarget{age}{%
\subsubsection{Age}\label{age}}

>>>>

\usepackage[no-weekday]{eukdate}
\usepackage{sourceserifpro}
\usepackage[scaled=0.86]{DejaVuSansMono}
\usepackage{float,bm,setspace}
\setstretch{1.2}

@@

{\centering \includegraphics{elections_conversation_files/figure-latex/intercept2-1}

\caption{Estimated intercept for each election, which represents the two-party preferred vote for an electorate with average characteristics.}\label{fig:intercept2}
\end{figure}

@@

\hypertarget{age}{%
\subsection{Age}\label{age}}

\begin{itemize}
\tightlist
\item
  Would it be possible to show how the correlation changes for different age brackets (ie. younger voters = more Labor, and this swings more to Liberal as the age brackets gets older)?
\item
  If not, can you go into more detail specific age brackets? Eg. Is it the over-65s that skew Liberal?
\end{itemize}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/age-1} \end{center}

@@

\hypertarget{age-1}{%
\subsubsection{Age}\label{age-1}}
